3 slides to convince you that it's endogenous TFP

### 2018-01-31 Latex/Basu_propositions/propositions.tex
edited Basu presentation to include empirical evidence

An IT productivity shock is $\lambda_{t+j}$ for some positive $j$.

@@

A news shock doesn't move relative prices if 
\begin{itemize}
\item No other exogenous shock hits the economy ($\Psi_t$ and $\lambda_t$ do not move);
\item the news shock doesn't change the relative marginal productivities of the two inputs in the two sectors, so that labor and capital are not reallocated from one sector to another.
\end{itemize}

>>>>

An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today.

@@

A news shock doesn't move relative prices if 
\begin{itemize}
\item the news shock doesn't change the relative marginal productivities of the two inputs in the two sectors, so that labor and capital are not reallocated from one sector to another.
\end{itemize}

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{+1 slide: evidence that $\gamma \neq 0$, i.e. that GPTs show up as spillovers}

Theoretical evidence
\begin{itemize}
\item Brynjolfsson, e.g. in Bloom et al. (2014): theory of IT as a GPT changing management practices.
\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the organization of production as a whole, so it's not just the firm's individual use of them that matters, but that of the economy as a whole.
\item Romer (1986): a production function with spillovers from human capital.
\end{itemize}

Empirical evidence
\begin{itemize}
\item Stiroh (2002 AER): industry-level data show that productivity gains from IT are not confined to industries producing IT.
\item Oliner \& Sichel (2000 JEP): growth accounting.
\item Black \& Lynch (2004, EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
\end{itemize}
